---
title: "EDA ASSIGNMENT"
author: "NAGASHYAM,MOUSAM MAJUMDER,RHISHIKESH PADOLE,OENDRIC BAIDYA,RICHITA VERMA"
date: "2 October 2018"
output: html_document
---


```{r include=FALSE}
library(dplyr)
library(ggplot2)
library(corrplot)
std_alc = read.csv("C:/Users/Administrator/Downloads/python_assgn/student-alcohol-consumption/student-por.csv")
sac=std_alc



```


### no.of male and female who consume alcohol

```{r warning=FALSE}
male_female_alc = std_alc %>%
  group_by(sex) %>%
  summarise(totalno = n())
male_female_alc
```
```{r warning=FALSE}
##graph
 ggplot(data = male_female_alc,aes(x = sex, y = totalno))+
geom_bar(stat = "identity",aes(fill=sex),width = 0.7)+
theme_bw()+
labs(x='Sex',y='total_no',subtitle='Gender base alcohol consumer',title='Bargraph')

```

### age wise alcohol consumption

```{r warning=FALSE}
male_female_alc = std_alc %>%
  group_by(age,sex) %>%
  summarise(total = n())
male_female_alc
```
```{r warning=FALSE}
p=ggplot(data=male_female_alc,aes(x=age,y=total))+geom_line(aes(col = sex))+geom_point()
p1=p+theme_bw()
p2=p1+labs(x='Ages',y='no_of_alcohol_consumer',title='Line-graph',subtitle='Age_based_alcohol_consumer')
p2
```


## alcohol consumption on schooling basis

## weekend alcohol consumption and day alcohol consumption

```{r warning=FALSE}
weekend = std_alc %>%
  group_by(Walc) %>%
  summarise(total = n()) 
weekend
day = std_alc %>%
  group_by(Dalc) %>%
  summarise(total = n())
day

```



```{r warning=FALSE}
ggplot(day,aes(x=Dalc,y=total))+geom_point(size=5,color=4)+geom_line(size=1,col=1)+theme_bw()+labs(title="day basis alcohol comparison",x='no of days',y='no.of student')
ggplot(weekend,aes(x=Walc,y=total))+geom_point(size=5,color=2)+geom_line(size=1,col=1)+
  labs(title='weekend basis alcohol comparison',x='no of weekend',y='no. of student')+theme_bw()
```


## students with romantic relationship consuming alcohol

```{r warning=FALSE}
relation_alcohol = std_alc %>%
  group_by(romantic) %>%
  summarise(total = n())
relation_alcohol

```
```{r warning=FALSE}
ggplot(data=relation_alcohol,aes(x=romantic,y=total))+geom_bar(stat = "identity",width=0.8,aes(fill= romantic))+theme_bw()+
labs(title="relation based alcholoic comparison", x="romanitc", y="no_of_alcohol")
```

### health of students after consuming the alohol

```{r warning=FALSE}
health_issues = std_alc %>%
  group_by(health) %>%
  summarise(no_of_drink = n())
health_issues
```
```{r warning=FALSE}
ggplot(data=health_issues,aes(x=reorder(health,-no_of_drink),y=no_of_drink,fill=health))+
  geom_bar(stat="identity",width=.5)+ theme_bw()+
  labs(x="health",y="no_of_drink",title="health condition based on no of drinks")+
  theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x = element_blank())
```

## no .of students who go with friends to drink alcohol

```{r warning=FALSE}
alc_frnds = std_alc %>%
  group_by(goout,sex) %>%
  summarise(total = n())
alc_frnds
```
```{r warning=FALSE}
ggplot(data=alc_frnds,aes(x=reorder(goout,-total),y=total,fill=sex))+geom_col()+theme_bw()+labs(title="no of students who with friends to drink alcohol",x="no.of.friends",y="student_no")
```

### students who drink alcohol after school in free time

```{r warning=FALSE}
after_school = std_alc %>%
  group_by(freetime) %>%
  summarise(total = n())
after_school
```
```{r warning=FALSE}
ggplot(after_school,aes(x=freetime,y=total))+geom_point(size=10,color=3)+geom_segment(aes(x=freetime, xend=freetime, y=0, yend=total),size=2)+theme_bw()+labs(title="freetime based students drinking comparison",x="free_time",y="no.of students")
```

# Pearson's Correlation
```{r warning=FALSE}

sac_num = sac %>% select(absences,G1,G2,G3)

num_corr = cor(sac_num)

num_corr

num_corr_plot = corrplot(num_corr, method = "square", type = "upper")

```

# Spearman's Correlation 
```{r warning=FALSE}

sac_fact = sac %>% select(traveltime,studytime,failures,famrel,freetime,goout,Dalc,Walc,health)

fact_corr = cor(sac_fact)

fact_corr

fact_corr_plot = corrplot(fact_corr, method = "square" ,type = "upper")

```


# Proportions 


# between mother(housewife) and address(rural Vs urban) (p = urban , q = rural)
```{r warning=FALSE}


x1 = sac %>% filter(address == "U" & Mjob == "at_home") %>% summarise(total = n())  


y1 = sac %>% filter(address == "R" & Mjob == "at_home") %>% summarise(total = n())


z1 = sac %>% filter(Mjob == "at_home") %>% summarise(total = n())

p1 = x1/z1

p1

q1 = y1/z1

q1

```
# (Conclusion : the proportion of student who's mother are housewife with urban locality is slightly higher than with rural locality,
#This means there is no relation between mother is housewife or not and locality is rural or urban)







# between gaurdian is father and mother (p = father , q = mother)
```{r warning=FALSE}

x2 = sac %>% filter(guardian == "father") %>% summarise(total = n())  


y2 = sac %>% filter(guardian == "mother") %>% summarise(total = n())


z2 = sac %>% summarise(total = n())

p2 = x2/z2

p2

q2 = y2/z2

q2

```
#(Conclusion : There is significant difference between the gaurdian is father or mother,
# This means being the guardian it may affects the student will consume alcohol
# Here, it indicates that students who's guardian is mother more tends to consume alcohol)









# between students takes alcohol wants to higher education or not (p = wants higher edu., q = doesn't want higher edu.)
```{r warning=FALSE}

x3 = sac %>% filter(higher == "yes") %>% summarise(total = n())  


y3 = sac %>% filter(higher == "no") %>% summarise(total = n())


z3 = sac %>%summarise(total = n())

p3 = x3/z3

p3

q3 = y3/z3

q3

```
# (Conclusion : The proportion of students wants to take higher education is more than those who doesn't want.)



# between students which has internet access at home or not (p = internet access , q = no internet access)
```{r warning=FALSE}

x4 = sac %>% filter(internet == "yes") %>% summarise(total = n())  


y4 = sac %>% filter(internet == "no") %>% summarise(total = n())


z4 = sac %>% summarise(total = n())

p4 = x4/z4

p4

q4 = y4/z4

q4


```

# (Conclusion : The proportion of students which has internet access at home is greater than those who doesn't have internet access.)








# between students which has attended nursery or not (p = attended nursery , q = not attended nursery)
```{r warning=FALSE}

x5 = sac %>% filter(nursery == "yes") %>% summarise(total = n())  


y5 = sac %>% filter(nursery == "no") %>% summarise(total = n())


z5 = sac %>% summarise(total = n())

p5 = x5/z5

p5

q5 = y5/z5

q5

```
# (Conclusion : The proportion of students attended nursery is greater than those who didn't attended.)








# between students which has paid extra class/tutions fees or not (p = paid extra class/tutions fees,
# q = not paid extra class/tutions fees)
```{r warning=FALSE}

x6 = sac %>% filter(paid == "yes") %>% summarise(total = n())  


y6 = sac %>% filter(paid == "no") %>% summarise(total = n())


z6 = sac %>% summarise(total = n())

p6 = x6/z6

p6

q6 = y6/z6

q6

```
# (Conclusion : The proportion of students which has paid extra class/tutions fees is less than those who paid.
# Means, students without extra class more tends to consume alcohol)






# between students which has attended nursery or not (p = attended nursery , q = not attended nursery)
```{r warning=FALSE}

x7 = sac %>% filter(famsup == "yes") %>% summarise(total = n())  


y7 = sac %>% filter(famsup == "no") %>% summarise(total = n())


z7 = sac %>% summarise(total = n())

p7 = x7/z7

p7

q7 = y7/z7

q7

```
# (Conclusion : The proportion of students who have family support for edu. is less than those who doesn't have.
# Mean, Self-ignited students doesn't lean towards alcohol consumption)





#Proportion Table
```{r warning=FALSE}
Proportion = c("Mother(Housewife) Vs Mother(no Housewife)", "Gaurdian(Father) Vs Gaurdian(Mother)",
               "Wants higher edu. Vs not","Internet Access Vs not","Attended nursery Vs not",
               "paid extra class fees Vs not","Educational support Vs not")
Success = c(p1,p2,p3,p4,p5,p6,p7)
Failure = c(q1,q2,q3,q4,q5,q6,q7)

table = data.frame(cbind(Proportion,Success,Failure))


View(table)

```


